\inputencoding{utf8}
\HeaderA{Log functions}{Optimbase Log functions}{Log functions}
\aliasA{optimbase.log}{Log functions}{optimbase.log}
\aliasA{optimbase.logshutdown}{Log functions}{optimbase.logshutdown}
\aliasA{optimbase.logstartup}{Log functions}{optimbase.logstartup}
\aliasA{optimbase.stoplog}{Log functions}{optimbase.stoplog}
\keyword{method}{Log functions}
%
\begin{Description}\relax
\code{optimbase.logstartup} initializes logging if verbose logging is enabled
(via the \code{verbose} element of the optimization object). If the logging
has already been initialized, it generates an error and stops the
optimization.

If verbose logging is enabled, \code{optimbase.log} prints the given message
in the console. If  verbose logging is disabled, it does nothing. If the
\code{logfile} element of the optimization object has been  set, it writes the
message into the file instead of writing to the console.

\code{optimbase.stoplog} prints the given stopping rule message if verbose
termination is enabled (via the \code{verbosetermination} element of the
optimization object). If verbose termination is disabled, it does nothing.

\code{optimbase.logshutdown} turns verbose logging off.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
  optimbase.logstartup(this = NULL)
  optimbase.log(this = NULL, msg = NULL)
  optimbase.stoplog(this = NULL, msg = NULL)
  optimbase.logshutdown(this = NULL)
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{this}] The optimization object.
\item[\code{msg}] The message to print.
\end{ldescription}
\end{Arguments}
%
\begin{Value}
All functions return the unchanged optimization object.
\end{Value}
%
\begin{Author}\relax
Author of Scilab optimbase module: Michael Baudin (INRIA - Digiteo)

Author of R adaptation: Sebastien Bihorel (\email{sb.pmlab@gmail.com})
\end{Author}
